### 2017-11-14 paper/sections/5_file-systems.tex
paper: addresses #13 and #15
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

%- strategy: cache all inodes on create
\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/compile-ops.png}\\
\caption{The file system metadata requests for a compile job shows distinct
workload phases, characterized by a dominant request type ({\it e.g.}, creates
for ``untar", lookups for ``make", etc.). Using a ParSplice cache management
policy for a workload like this in file systems could reduce memory pressure
without sacrificing performance.  \label{fig:compile-ops}}
\end{figure}

>>>>

%- strategy: cache all inodes on create
\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/compile-ops.png}\\
\caption{File system metadata requests for a compile job show workload phases
characterized by a dominant request type ({\it e.g.}, creates for ``untar").
Using ParSplice cache management policies for these types of workloads would
reduce memory pressure without sacrificing performance.
\label{fig:compile-ops}}
\end{figure}
